Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-23 analysis/paper/paper.Rmd
Remove patchwork, use cowplot instead

```{r, setup, echo=FALSE, message=FALSE, include=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "cowplot",
  "dplyr",
  "english",
  "extrafont",
  "flextable",
  "ggpubr",
  "grDevices",
  "here",
  "janitor",
  "knitr",
  "officer",
  "parameters",
  "patchwork",
  "posterior",
  "report",
  "rsvg",
  "rstan",
  "tidyr",
  "tools"
)

@@

```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public. A test for equivalence was unable to detect any clear differences between *Phytopathology*&reg; and all other journals sharing computational materials (code). However, a test for equivalence found that articles in *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*&reg;. Intervals in grey have a median value less than that of *Phytopathology*&reg;, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*&reg;. The region of practical equivalence (ROPE) is shown between two dotted lines. If the entire distribution falls within the ROPE, the hypothesis is accepted. If the entire distribution falls outside the ROPE, the hypothesis is rejected. In some cases the data do not provide a definitive answer and the decision on H0 is undecided.', cache=FALSE, fig.env='figure'}
m_f1_eq <- equivalence_test(m_f1)
m_f2_eq <- equivalence_test(m_f2)

@@

m_g1_eq <- equivalence_test(m_g1)
m_g2_eq <- equivalence_test(m_g2)

@@

```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence was undecided on any detectable effects of impact factor. The region of practical equivalence (ROPE) is shown between two dotted lines. If the entire distribution falls within the ROPE, the hypothesis is accepted. If the entire distribution falls outside the ROPE, the hypothesis is rejected. In some cases the data do not provide a definitive answer and the decision on H0 is undecided. Here, impact factor is a continous variable to determine if greater or lesser impact factor values affect the likelyhood of sharing code and data.', cache=FALSE, fig.env='figure'}
m_h1_eq <- equivalence_test(m_h1)
m_h2_eq <- equivalence_test(m_h2)

>>>>

```{r, setup, echo=FALSE, message=FALSE, include=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "cowplot",
  "dplyr",
  "english",
  "extrafont",
  "flextable",
  "ggpubr",
  "grDevices",
  "here",
  "janitor",
  "knitr",
  "officer",
  "parameters",
  "posterior",
  "report",
  "rsvg",
  "rstan",
  "tidyr",
  "tools"
)

@@

```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public. A test for equivalence was unable to detect any clear differences between *Phytopathology*&reg; and all other journals sharing computational materials (code). However, a test for equivalence found that articles in *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*&reg;. Intervals in grey have a median value less than that of *Phytopathology*&reg;, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*&reg;. The region of practical equivalence (ROPE) is shown between two dotted lines. If the entire distribution falls within the ROPE, the hypothesis is accepted. If the entire distribution falls outside the ROPE, the hypothesis is rejected. In some cases the data do not provide a definitive answer and the decision on H0 is undecided.', cache=FALSE, fig.env='figure'}
m_f1_eq <- equivalence_test(m_f1, rule = "bayes")
m_f2_eq <- equivalence_test(m_f2, rule = "bayes")

@@

m_g1_eq <- equivalence_test(m_g1, rule = "bayes")
m_g2_eq <- equivalence_test(m_g2, rule = "bayes")

@@

```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence was undecided on any detectable effects of impact factor. The region of practical equivalence (ROPE) is shown between two dotted lines. If the entire distribution falls within the ROPE, the hypothesis is accepted. If the entire distribution falls outside the ROPE, the hypothesis is rejected. In some cases the data do not provide a definitive answer and the decision on H0 is undecided. Here, impact factor is a continous variable to determine if greater or lesser impact factor values affect the likelyhood of sharing code and data.', cache=FALSE, fig.env='figure'}
m_h1_eq <- equivalence_test(m_h1, rule = "bayes")
m_h2_eq <- equivalence_test(m_h2, rule = "bayes")
